Learning Excursion Sets of Vector-valued Gaussian Random Fields for Autonomous Ocean Sampling

### 2021-03-11 main_web.tex
Updates from Overleaf

We denote by $\gp$ a vector-valued random field indexed by some
arbitrary domain $\domain$, and assume values of the field at any
fixed location $\x \in \domain$, denoted $\gp[\x]$, to be a
$\no$-variate random vector ($\no\geq 2$). In the river plume
characterization case, $\domain$ is a prescribed domain in
Trondheimsfjord, Norway (for the purpose of our AUV application, a
discretization of a $2$-dimensional domain at fixed depth is
considered), and $\no=2$ with responses of temperature and salinity. A
multivariate GRF model is assumed for $\gp$. To motivate concepts,
Fig.~\ref{fig:real_temp} and \ref{fig:real_sal} show a realization of such a
vector-valued GRF on $\domain=[0,1]^2$. Fig.~\ref{fig:jointex_roi} represents a by-product of interest derived from these
realizations, namely regions: i) in red, where both temperature and salinity are high (i.e., exceeding respective thresholds), indicative of ocean water, ii) in white, where both temperature and salinity are low, indicative of riverine water, and iii) in light-red, where one variable is above and the other below their respective thresholds, indicative of mixed waters.

\begin{figure}[!b] 
\centering 
\subfigure[Temperature.]{\includegraphics[
height=0.27\textwidth,keepaspectratio]{Figures/intro_temp.png}\label{fig:real_temp}}
\subfigure[Salinity.]{\includegraphics[
height=0.27\textwidth,keepaspectratio]{Figures/intro_sal.png}\label{fig:real_sal}}
\subfigure[Regions of interest.]{\includegraphics[
height=0.27\textwidth,keepaspectratio]{Figures/intro_excu.png}\label{fig:jointex_roi}}
\caption{Realization of a bivariate GRF (display (a) and (b)) and ES above some threshold (c). Joint excursion in red and excursion of a single variable in light-red.}
\label{example_excu}
\end{figure}

@@

Letting $\gp[\spatloc,\ell]$ denote the $\ell\text{-th}$ component of
$\gp[\spatloc]$ ($1\leq \ell\leq \no$), we use the term
\textit{generalized location} for the couple $x=(\spatloc,\ell)$.
%Given such a generalized location notation $x$,  
The notation $\gp[x]$ will be used to denote $\gp[\spatloc,\ell]$ 
and
%
will allow us to think of $\gp$ as a scalar-valued random field indexed by $\domain \times \{1\dots,p\}$, which will give the co-Kriging equations a particularly simple form that parallels the one of univariate Kriging. 
The letters $\spatloc$ and $\ell$ will be used for spatial locations and response indices respectively.
%
Furthermore, boldface letters will be used to denote concatenated
quantities corresponding to batches of observations.  Given a dataset
consisting of
$q$ observations at spatial locations
$\bm{\spatloc}=(\spatloc_1,\dots,\spatloc_q) \in
\domain^q$ and response indices $\bm{\ell}=(\ell_1,\dots, \ell_q)\in
\lbrace 1, ..., \no\rbrace^q$, %$i=1, ..., q$,
we use the concatenated notation
\begin{align*}
\bm{x}:=%(\bm{\spatloc}, \bm{\ell}):= 
(x_1,\dots, x_q),~\text{with }x_i=(\spatloc_i,\ell_i).
\end{align*}
We also compactly denote the field values at those different locations by
\begin{align*}
\gp[\bm{x}]:=
\left(\gp[\spatloc_1,\ell_1], ...,
\gp[\spatloc_q,\ell_{q}]\right) \in \mathbb{R}^{q}.
\end{align*}

@@

Given a GRF $\gp$ and observations of some of its components at
locations in the domain, one can predict the value of the field at
some unobserved location $\spatloc\in \domain$ by using the
conditional mean of $\gp[\spatloc]$, given the data. This
coincides with co-Kriging equations, which tell us precisely how to
compute conditional means and covariances.  We will present a general
form of co-Kriging, in the sense that it allows inclusion of several
(batch) observations at a time; observations at a given location
$u \in \domain$ may only include a subset of the components of
$\gp[\spatloc]\in\mathbb{R}^{\no}$ (heterotopic).

>>>>

We denote by $\gp$ a vector-valued random field indexed by some
arbitrary domain $\domain$, and assume values of the field at any
fixed location $\x \in \domain$, denoted $\gp[\x]$, to be a
$\no$-variate random vector ($\no\geq 2$). In the river plume
characterization case, $\domain$ is a prescribed domain in
Trondheimsfjord, Norway (for the purpose of our AUV application, a
discretization of a $2$-dimensional domain at fixed depth is
considered), and $\no=2$ with responses of temperature and salinity. A
multivariate GRF model is assumed for $\gp$. To illustrate these concepts,
Fig.~\ref{fig:real_temp} and \ref{fig:real_sal} show a realization of such a
vector-valued GRF on $\domain=[0,1]^2$. Fig.~\ref{fig:jointex_roi} represents a by-product of interest derived from these
realizations, namely regions: i) in red, where both temperature and salinity are high (i.e., exceeding respective thresholds), indicative of ocean water, ii) in white, where both temperature and salinity are low, indicative of riverine water, and iii) in light-red, where one variable is above and the other below their respective thresholds, indicative of mixed waters.

\begin{figure}[!b] 
\centering 
\subfigure[Temperature]{\includegraphics[
height=0.27\textwidth,keepaspectratio]{Figures/intro_temp.png}\label{fig:real_temp}}
\subfigure[Salinity]{\includegraphics[
height=0.27\textwidth,keepaspectratio]{Figures/intro_sal.png}\label{fig:real_sal}}
\subfigure[Regions of interest]{\includegraphics[
height=0.27\textwidth,keepaspectratio]{Figures/intro_excu.png}\label{fig:jointex_roi}}
\caption{Realization of a bivariate GRF (display (a) and (b)) and ES above some threshold (c). Joint excursion in red and excursion of a single variable in light-red.}
\label{example_excu}
\end{figure}

@@

Letting $\gp[\spatloc,\ell]$ denote the $\ell\text{-th}$ component of
$\gp[\spatloc]$ ($1\leq \ell\leq \no$), we use the term
\textit{generalized location} for the couple $x=(\spatloc,\ell)$.
%Given such a generalized location notation $x$,  
The notation $\gp[x]$ will be used to denote $\gp[\spatloc,\ell]$ 
and
%
will allow us to think of $\gp$ as a scalar-valued random field indexed by $\domain \times \{1\dots,p\}$, which will give the co-Kriging equations a particularly simple form that parallels the one of univariate Kriging. 
The letters $\spatloc$ and $\ell$ will be used for spatial locations and response indices, respectively.
%
Furthermore, boldface letters will be used to denote concatenated
quantities corresponding to batches of observations.  Given a dataset
consisting of
$q$ observations at spatial locations
$\bm{\spatloc}=(\spatloc_1,\dots,\spatloc_q) \in
\domain^q$ and response indices $\bm{\ell}=(\ell_1,\dots, \ell_q)\in
\lbrace 1, ..., \no\rbrace^q$, %$i=1, ..., q$,
we use the concatenated notation
\begin{align*}
\bm{x}:=%(\bm{\spatloc}, \bm{\ell}):= 
(x_1,\dots, x_q),~\text{with }x_i=(\spatloc_i,\ell_i).
\end{align*}
We also compactly denote the field values at those different locations by
\begin{align*}
\gp[\bm{x}]:=
\left(\gp[\spatloc_1,\ell_1], ...,
\gp[\spatloc_q,\ell_{q}]\right) \in \mathbb{R}^{q}.
\end{align*}

@@

Given a GRF $\gp$ and observations of some of its components at
locations in the domain, one can predict the value of the field at
some unobserved location $\spatloc\in \domain$ by using the
conditional mean of $\gp[\spatloc]$, given the data. This
coincides with co-Kriging equations, which tell us precisely how to
compute conditional means and covariances.  We will present a general
form of co-Kriging, in the sense that it allows for the inclusion of several
(batch) observations at a time; observations at a given location
$u \in \domain$ may only include a subset of the components of
$\gp[\spatloc]\in\mathbb{R}^{\no}$ (heterotopic).
